\documentclass[11pt,letterpaper]{article}

\usepackage[margin=1in]{geometry}
\usepackage{termcal}
\usepackage{enumitem}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{color}
\usepackage{multirow}
\usepackage{multicol}

\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}

\title{16.S897: Spacecraft Attitude Determination and Control}
\author{Spring 2026}
\date{}

\begin{document}

\maketitle

%\noindent 
%\textbf{Course website:} \href{https://optimalcontrol.ri.cmu.edu/}{optimalcontrol.ri.cmu.edu}

\section*{Course Description}

This course is all about attitude: pointing, slewing, spinning, and (occasionally, but hopefully not too often...) tumbling. We will discuss:
\begin{itemize}
\item Attitude representations and how to effectively parameterize attitude in different situations.
\item How to model and simulate spacecraft attitude dynamics.
\item How to estimate attitude from sensor measurements.
\item How to manage a spacecraft's attitude with both passive physics and closed-loop control.
\end{itemize}
The course will be based around a project in which each student analyzes the attitude determination and control system (ADCS) for a spacecraft mission.

\medskip
\noindent
\textbf{Prerequisites:} We will assume linear algebra skills and basic familiarity with the content of 16.31, as well as prior experience with a high-level programming language like Python, MATLAB, or Julia.

\section*{Instructor}

\begin{center}
\begin{tabular}{l l l}
	Prof. Zac Manchester & \textbf{Email:} \href{mailto:zacm@mit.edu}{zacm@mit.edu} & \textbf{Office:} 31-243
\end{tabular}
\end{center}

\section*{Logistics}

\begin{itemize}
	\item Lectures will be held \textbf{Tuesdays and Thursdays 12:30--2:00} Eastern time in \textbf{33-422}. Lectures will also be live streamed on zoom and recorded for later viewing.
	%\item Recitation will be held Fridays on Zoom at 11 AM.
	\item Office hours will be \todo{based on survey}.
	\item Homework assignments will be due by \todo{due date}. Two weeks will be given to complete each assignment.
	\item Short quizzes will occasionally be assigned to assess student comprehension. These will be graded only based on completion.
	% \item GitHub will be used to distribute assignments and GradeScope will be used for submissions.
	\item Slack will be used for general discussion and Q\&A outside of class and office hours.
	\item There will be no exams. Instead, students will compile a final report based on analysis done in each homework assignment.
\end{itemize}

\newpage 
\section*{Learning Objectives}
By the end of this course, students should be able to do the following:
\begin{enumerate}
	\item Model and simulate the attitude dynamics of a spacecraft
	\item Analyze stability of spacecraft attitude dynamics
	\item Estimate the attitude of a spacecraft from sensor measurements
	\item Design feedback controllers to stabilize spacecraft attitude
	\item Design slewing maneuvers to point a spacecraft at a desired target
	\item Characterize the performance of a closed-loop attitude control system
	\item Select sensors and actuators to meet mission requirements
\end{enumerate}

\section*{Learning Resources}

There is no textbook for this course. Video recordings of lectures and lecture notes will be posted online. The following books are good references for some of the topics discussed in the course that you may want to refer to, but are not required:

\begin{enumerate}
	\item M. Paluszek, \textit{ADCS -- Spacecraft Attitude Determination and Control}, Elsevier, 2023.
	\item F. Markley and J. Crassidis, \textit{Fundamentals of Spacecraft Attitude Determination and Control}, Springer, 2014.
	\item P. Hughes, \textit{Spacecraft Attitude Dynamics}, Dover, 2004.
	\item J. Wertz, \textit{Spacecraft Attitude Determination and Control}, Kluwer, 1978.
\end{enumerate}
\section*{Assignments}

\begin{itemize}
	\item Short quizzes will be assigned once per week. These are intended as a diagnostic tool for the instructor and should take no more than 15 minutes to complete.
	\item Every two weeks students will be asked to complete a homework assignment that includes analysis of some aspect of the ADCS design for a spacecraft mission of their choice (chosen on the first homework). A write-up of this analysis will be reviewed by the instructor and feedback will be returned to students the following week.
	\item At the end of the semester, homework assignments will be compiled into a final report. There will be no exams in this course.
\end{itemize}

\section*{Grading}

Grading will be based on:
\begin{itemize}
	\item 40\% Homework
	\item 40\% Final Report
	\item 15\% Quizzes
	\item 5\% Participation
\end{itemize}
Attendance during lectures is not required to earn a full participation grade. Students can also participate through any combination of office hours, Slack discussions, project presentations, and by offering constructive feedback about the course to the instructors.


\section*{Course Policies}

\textbf{Late Homework:} Students are allowed a budget of six late days for turning in homework with no penalty throughout the semester. They may be used together on one assignment, or separately on multiple assignments. Beyond these six days, no other late homework will be accepted.

\section*{Tentative Schedule}

\begin{tabular}{c|c|c|c}
	Week & Dates & Topics & Assignments \\
	\hline
	\multirow{2}{*}{1} & Feb 3 & 
        Course Overview, \& Attitude Intro & Survey \\
	 & Feb 5 & Representations, SO(3), and Quaternions &  HW1 Out\\
	\hline
	\multirow{2}{*}{2} & Feb 10 &
        Rigid Body Dynamics &  \\
	 & Feb 12 & Gyrostat Dynamics &  \\
	\hline
	\multirow{2}{*}{3} & Feb 17 &
        Damping and Environmental Perturbations & HW1 Due \\
	 & Feb 19 &  & HW2 Out \\
	\hline
	\multirow{2}{*}{4}  & Feb 24 &
        Spinning Spacecraft and Stability &  \\
	 & Feb 26 & Numerical Simulation &  \\
	\hline
	\multirow{2}{*}{5}  & Mar 3 &  Attitude Determination Sensors & HW2 Due \\
	 & Mar 5 & TRIAD & HW3 Out \\
	\hline
	\multirow{2}{*}{6}  & Mar 10 & Statistical Estimation &  \\
	 & Mar 12 & Optimizing with Attitude &  \\
	\hline
	\multirow{2}{*}{7}  & Mar 16 & Wahba's Problem
         & HW3 Due \\
	 & Mar 18 & Nonlinear Least-Squares \& Convex Relaxations & \\
	\hline
	\multirow{2}{*}{8}  & Mar 24 & 
        \textcolor{red}{No Class --- Spring Break} & \\
	 & Mar 26 & \textcolor{red}{No Class --- Spring Break} &   \\
	\hline
	\multirow{2}{*}{9}  & Mar 31 & Kalman Filters
         & HW4 Out \\
	 & Apr 2 & Multiplicative \& Invariant EKF &  \\
	\hline
	\multirow{2}{*}{10}  & Apr 7 & \todo{Guest Lecture - Case Studies} 
         &  \\
	 & Apr 9 & \todo{Guest Lecture - Fault Recovery and Anomalies}  &   \\
	 \hline
	\multirow{2}{*}{11}  & Apr 14 & Passive Attitude Control Methods
         & HW4 Due \\
	 & Apr 16 & Attitude Control Actuators &  HW5 Out \\
	 \hline
	\multirow{2}{*}{12}  & Apr 21 & Feedback Controllers
         &   \\
	 & Apr 23 & Stabilization and Tracking &   \\
	 \hline
	\multirow{2}{*}{13}  & Apr 28 & Designing Slew Maneuvers
         & HW5 Due \\
	 & Apr 30 & Optimal Control &   \\
	 \hline
	\multirow{2}{*}{14}  & May 5 & Performance Analysis
         &  \\
	 & May 7 & Sensor and Actuator Calibration &   \\
	 \hline
	\multirow{2}{*}{14}  & May 12 &
        Small Satellite Case Studies &  \\
	 &  &  &   \\
\end{tabular}


\end{document}
